R for Clinical Study Reports and Submission

### 2021-11-07 project-folder.Rmd

```
vignettes
├── adam_data
├── tlf
├── tlf-01-disposition.Rmd
├── tlf-02-population.Rmd
├── tlf-03-baseline.Rmd
├── tlf-04-efficacy.Rmd
├── tlf-05-ae-summary.Rmd
└── tlf-06-ae-spec.Rmd
```

@@

- create a `renv.lock` file to save the state of package versions.
- create a `renv` folder to manage R packages for a project.

>>>>

```
vignettes
├── data-adam
├── tlf
├── tlf-01-disposition.Rmd
├── tlf-02-population.Rmd
├── tlf-03-baseline.Rmd
├── tlf-04-efficacy.Rmd
├── tlf-05-ae-summary.Rmd
└── tlf-06-ae-spec.Rmd
```

@@

- create a `renv.lock` file to save the state of package versions.
- create a `renv/` folder to manage R packages for a project.
